---
title: "W_UP_01"
author: "Sierra Lander"
date: "summer 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups in 2 mins of line vs skill players

$H_A$: The average number of pushups in 2 mins done by line players s is statistically different than that of skill players.

# Methods

pushups is a numerical variable 

position is a categorical variable 

We use helper file num~cat




<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

## Descriptive Results

### Graphical Descriptive Results


```{r}
boxplot(pushups~position,data=mydata)
```




The graph shows that the Skill players on average can do more pushups than the line players (~50 vs ~20)





### Numerical Descriptive Results



```{r}
favstats(pushups~position,data=mydata)
```



The fav stats test shows that the average for amount of pushups in 2 mins for line players is 14.5 and average for Skill players is 47.5  




<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

