---
title: "W_UP_01"
author: "Sierra Lander"
date: "summer 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups in 2 mins of line vs skill players

$H_A$: The average number of pushups in 2 mins done by line players s is statistically different than that of skill players.

# Methods

pushups is a numerical variable 

position is a categorical variable 

We use helper file num~cat




<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

## Descriptive Results

### Graphical Descriptive Results


```{r}
boxplot(pushups~position,data=mydata)
```




The graph shows that the Skill players on average can do more pushups than the line players (~50 vs ~20)





### Numerical Descriptive Results



```{r}
favstats(pushups~position,data=mydata)
```



The fav stats test shows that the average for amount of pushups in 2 mins for line players is 14.5 and average for Skill players is 47.5  




<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
t.test(pushups~position,data=mydata)
```

The data shows that the p-value is 0.0000094 this means that we must reject H0 because it is less than 0.05 




# Discussion and Conclusion

In conclusion the average number of pushups in 2 mins done by line players  is statistically different than that of skill players. This is because acording to the fav stats test the average for line players is 14.5 and for skill players 47.5 The t- test showed that the p-value was less than 0.05 wich also shows that we must reject H0 






